\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-23 draft.tex
paste in final argument for proof of prop:2NNB from two-groups

In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b_{-\frac{1}{2}}$, we know that $Z < 0$. Note that this is due to the construction of the problem. This means $e^Z < 1$. In this case,
	\begin{itemize}
		\item Equation~\ref{eq:1} is consistent with $X>Y>0$, $X>0>Y$, or $0>X>Y$.
		\item Equation~\ref{eq:2} is consistent with $Y>X>0$, $Y>0>X$, or $0>Y>X$.
	\end{itemize}
The second order conditions imply that both $X$ and $Y$ are positive, thus it must be that $X = Y > 0$ (see below). Note that once this is known, one can go back to, for instance, Equations~\ref{eq:baseX} and substitute for one of the variables. Given that $Z=0$, with a particular value of $\left(\alpha,W_B\right)$, the solution gives the values of the two relevant bribes.

>>>>

In this case where the non-negativity constraint binds for the variable associated with $Z$, that is $b\left(\frac{1}{2}\right)$, there are three possibilities, $Z=0$, $Z>0$ and $Z<0$. I will take each in turn.
\begin{enumerate}
	\item When $Z = 0$, $e^Z = 1$. Then the only values of $X$ and $Y$ with which both Equation~\ref{eq:1} and \ref{eq:2} are consistent are $X=Y$.
		\begin{itemize}
			\item Note that this is the only case in which $e^{-2Z} =1$, i.e. $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = 0$. In the other two cases, the right hand side of \ref{eq:soc} is positive so that the two second derivatives on the left hand side must be either both positive or both negative. This means that $X$ and $Y$ must be either both positive or both negative.
		\end{itemize}
	\item When $Z > 0$, $e^Z > 1$. In this case, $X$ and $Y$ must be positive since they are greater than $Z$.
		\begin{itemize}
			\item Equation~\ref{eq:1} is consistent with $Y\geq X\geq 0$.
			\item Equation~\ref{eq:2} is consistent with $X \geq Y \geq 0$.
			\item Since both equations must hold, we have $X=Y \geq 0$
		\end{itemize}
	\item When $Z < 0$, $e^Z < 1$. In this case,
			\begin{itemize}
				\item Equation~\ref{eq:1} is consistent with $X\geq Y\geq 0$ or $0 \geq Y \geq X$.
				\item Equation~\ref{eq:2} is consistent with $Y \geq X \geq 0$ or $0 \geq X \geq Y$.
				\item Since both equations must hold, we have either $X=Y \geq 0$ or $X=Y \leq 0$
		\end{itemize}
\end{enumerate}
